---
title: 'Project 2: Building a Safer Health System'
output:
  pdf_document: default
  html_notebook: default
  word_document: default
---

```{r}
if(!require(pacman)) install.packages(pacman)
library(pacman)
pacman::p_load(tidyverse, psych, readxl, dplyr, rpart, rattle)
```

```{r}
#Plugs file into variable
ICUEvents <- read_excel("ICUEvents.xlsx")
```

```{r}
names(ICUEvents)
```

```{r}
newICU1 <- ICUEvents
newICU1 <- newICU1[complete.cases(newICU1["Type-of-error"]), ]
```

```{r}
# Remove useless column
newICU1 <- subset(newICU1, select= -...11)
newICU2 <- ICUEvents

```


```{r}
# Lets you view document
view(newICU1)
```

```{r}
#Summarizes doc
summary(newICU1)
```

```{r}
#Gives you the data types of features
str(newICU1)
```

```{r}
# Factor 
newICU1$`Date-of-error` <- as.Date(newICU1$`Date-of-error`, tryFormats = c("%d-%m-%Y", "%d/%m/%y"))
#newICU1$`Time-of-error` <- as.Date(newICU1$`Time-of-error`, tryFormats = c("%h:%m"))
#newICU1
#newICU1$`Staff-type-initiated-error`[newICU1$`Staff-type-initiated-error`.con]

```

```{r}
newICU1$`Error-category` <- factor(newICU1$`Error-category`)
```

```{r}
newICU1$`Type-of-error` <- factor(newICU1$`Type-of-error`)
newICU1$`Cause-of-error` <- factor(newICU1$`Cause-of-error`)
```

```{r}
newICU1$`Contributing-factor` <- factor(newICU1$`Contributing-factor`)
newICU1$`Medication-process-node` <- factor(newICU1$`Medication-process-node`)
newICU1$`Staff-type-initiated-error` <- factor(newICU1$`Staff-type-initiated-error`)
newICU1$`Staff-type-perpetuated-error` <- factor(newICU1$`Staff-type-perpetuated-error`)
newICU1$`Action-taken` <- factor(newICU1$`Action-taken`)
newICU1$`Staff-type-discovered-error` <- factor(newICU1$`Staff-type-discovered-error`)
newICU1$`Day-of-week` <- factor(newICU1$`Day-of-week`)
```

```{r}
summary(newICU1)
```

```{r}
count_day_week <- newICU1 %>%
  count(`Day-of-week`)

ggplot(count_day_week, aes(x = `Day-of-week`, y = n)) +
         geom_bar(stat = 'identity') + geom_text(aes(label = n, vjust = -.45) )
```

```{r}
count_error_category <- newICU1 %>%
  count(`Error-category`)

```

```{r}
ggplot(count_error_category, aes(x = `Error-category`, y = n)) +
         geom_bar(stat = 'identity') + geom_text(aes(label = n, vjust = -.45) )
  
```


```{r}
Improper_doseICU1 <- subset(newICU1, `Type-of-error` =='Improper dose/quantity')
Improper_doseICU1 <- subset(Improper_doseICU1, select= c(`Type-of-error`, `Error-category`,   `Day-of-week`, `Contributing-factor`, `Medication-process-node`, `Location-of-error`))
```

```{r}
set.seed(1000)
Improper_doseICU1$`Day-of-week` <- as.factor(Improper_doseICU1$`Day-of-week`)
```

```{r}
fit <- rpart( `Medication-process-node` ~  `Day-of-week` + `Location-of-error`, data=Improper_doseICU1, method="class") 

fancyRpartPlot(fit)
```
```{r}
pacman::p_load(tm, wordcloud, e1071, gmodels)
```

```{r}
ICU_data <- subset(newICU2, select= c(`Type-of-error`, `Description-of-error`))
ICU_data$isImproperDose <- ICU_data$`Type-of-error`
ICU_data$`Type-of-error` <- factor(ICU_data$`Type-of-error`)
```

```{r}

ICU_data <- mutate(ICU_data, isImproperDose = ifelse(as.character(isImproperDose) != "Improper dose/quantity", "Other", as.character(isImproperDose)))

ICU_data <- subset (ICU_data, select = -`Type-of-error`)
```

### Factor
```{r}
ICU_data$isImproperDose <- factor(ICU_data$isImproperDose)
```
### Frequency
```{r}
table(ICU_data$isImproperDose)
```


```{r}

prop.table(table(ICU_data$isImproperDose))

```
## Corpus
```{r}
corpus <- Corpus(VectorSource(ICU_data$`Description-of-error`))
# str(corpus)
```

```{r}
corpus[1:10] %>%
  inspect()
```

### Clean
#### Set to Lower Case
```{r}
clean_corpus <- tm_map(corpus, tolower)
clean_corpus[1:10] %>%
  inspect()
```
#### Remove Numbers
```{r}
clean_corpus1 <- clean_corpus %>%
  tm_map(removeNumbers)

clean_corpus1[1:10] %>%
  inspect()
```
#### Remove Stop Words
```{r}
clean_corpus2 <- tm_map(clean_corpus1, removeWords, stopwords())
clean_corpus2[1:10] %>%
  inspect()
```
#### Remove Punctuation
```{r}
clean_corpus3 <- tm_map(clean_corpus2, removePunctuation)
clean_corpus3[1:10] %>%
  inspect()
```
#### Remove White Space
```{r}
clean_corpus4 <- tm_map(clean_corpus3, stripWhitespace)
clean_corpus4[1:10] %>%
  inspect()
```
### Document Term Matrix from tm package
```{r}
dmt <- DocumentTermMatrix(clean_corpus4)
dmt
# View(dmt)
```
## Creating Training and Test Datasets
### Splitting the Data Frame
```{r}
ICU_data.max_size <- nrow(ICU_data)
ICU_data$isImproperDose <- factor(ICU_data$isImproperDose)
test.size <- round(ICU_data.max_size * .3)
train.size <- round(ICU_data.max_size * .7)
train.df <- ICU_data[1:train.size,]
test.df <- ICU_data[(train.size+1):ICU_data.max_size,]

```

```{r}
clean_corpus.max_size <- length(clean_corpus4)
clean_corpus_test.size <- round(clean_corpus.max_size * .3)
clean_corpus_train.size <- round(clean_corpus.max_size * .7)
clean_corpus_train.df <- clean_corpus4[1:clean_corpus_train.size ]
clean_corpus_test.df <- clean_corpus4[(clean_corpus_train.size +1):clean_corpus.max_size]
```

### Splitting the Document Term Matrix
```{r}
dmt.max_size <- length(dmt)
dmt_test.size <- round(dmt.max_size * .3)
dmt_train.size <- round(dmt.max_size * .7)
dmt_train <- dmt[1:dmt_train.size,]
dmt_test <- dmt[(dmt_train.size+1):dmt.max_size,]
```

### Compare Frequencies
```{r}
prop.table(table(ICU_data$isImproperDose))
```

```{r}
prop.table(table(train.df$isImproperDose))
```

```{r}
prop.table(table(test.df$isImproperDose))
```

### Subset
#### Subset Improper dose/quantity
```{r}
Improper <- subset(train.df, isImproperDose=="Improper dose/quantity")
```

#### Subset Other
```{r}
Other <- subset(train.df, isImproperDose=="Other")
```
## Find Frequent Terms
### Words That Have a Frequency of 5 or More
```{r}
Dict <- findFreqTerms(dmt_train, 1)
Dict
```


```{r}
matrix_train <- DocumentTermMatrix(clean_corpus_train.df, list(dictionary=Dict))
```

```{r}
matrix_test <- DocumentTermMatrix(clean_corpus_test.df, list(dictionary=Dict))
```

```{r}
convert_counts <- function(x) {
  x <- ifelse(x > 0, 1, 0) 
  x <- factor(x, levels = c(0,1),
              label= c("Yes","No"))
  return(x)
}
```

### Apply convert_counts
```{r}
convert_train1 <- apply(matrix_train, MARGIN = 2, convert_counts)
convert_test1 <-apply(matrix_test, MARGIN = 2, convert_counts)
```

#### Check data using str
```{r}
str(convert_train1)
```

```{r}
str(convert_test1)
```
## Building the Classifier
```{r}
classifier <- naiveBayes(convert_train1, train.df$isImproperDose)

```
## Making Predictions
```{r}
test_predict <- predict(classifier, convert_test1)
```
## Crosstables
```{r}
cross_table <- CrossTable(test_predict, 
           test.df$isImproperDose,
           prop.chisq = TRUE, 
           prop.t = TRUE, 
           prop.c = TRUE, 
           prop.r = TRUE, 
           dnn = c('predicted', 'actual'))
```


